---
title: "Assignment_3"
author: "Purna Sai Kiran"
date: "March 7, 2021"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

Loading the required Universal Bank Data to work on the Personal Loan Probability Using Naive Bayes Model and studying the structure of the data
```{r}
setwd("E:\\Kent\\Fundamentals of Machine Learning - Prof Murali Shanker\\Assignment_3")
cust_data <- read.csv("UniversalBank.csv")
```

Converting the integer variables into factors since Naive Bayes need categorical variables for computing probability.


```{r}
cust_data$CreditCard <- as.factor(cust_data$CreditCard)
cust_data$Online <- as.factor(cust_data$Online)
cust_data$Personal.Loan <- as.factor(cust_data$Personal.Loan)
```

We are using Caret Library. Data partition is done with 60:40 ratio for Train and Test data respectively. We have also calculated the rows to verify the partition is as per the specified ratio

```{r, message=FALSE}
library(caret)
set.seed(1000)
Train_Index <- createDataPartition(cust_data$ID, p = 0.6, list = FALSE)
Train_df <- cust_data[Train_Index,]
nrow(Train_df)
Valid_df <- cust_data[-Train_Index,]
nrow(Valid_df)
```

Q1 : Create a pivot table for the training data with Online as a column variable, CC as a row variable, and Loan as a secondary row variable. The values inside the table should convey the count.

```{r}
Pivot <- table(Train_df$Personal.Loan,Train_df$CreditCard)
Pivot
pivot_df <- as.data.frame(Pivot)
colnames(pivot_df) <- c("PersonalLoan", "CreditCard","Online")
pivot_df

```
A : Here we created a pivot using table function.We have also named the columns for easy reference. The pivoting is done on Train data alone. The Probability


Q2 : Consider the task of classifying a customer who owns a bank credit card and is actively using online banking services. Looking at the pivot table, what is the probability that this customer will accept the loan offer? 
```{r}
Prob_POCC <- 83/(790+83)*100 #From the table the probability for a person accepting a loan and having a credit card issued and taken online services
Prob_POCC

```
A : From the available table we have identified that the probability of a customer accepting a loan when the customer has a credit card and online facility is 9.51%

Q3 : Create two separate pivot tables for the training data. One will have Loan (rows) as a function of Online (columns) and the other will have Loan (rows) as a function of CC.
```{r}
Pivot_PO <- table(Personal.Loan=Train_df$Personal.Loan, Online = Train_df$Online)
Pivot_PO

Pivot_PCC <- table(Personal.Loan = Train_df$Personal.Loan, CreditCard = Train_df$CreditCard)
Pivot_PCC

```

We have used the table() function to create separate pivot tables with Loan as row function for both Online and CreditCard variables in columns. 

Q4 : D. Compute the following quantities [P(A | B):
i. P(CC = 1 | Loan = 1) 
ii. P(Online = 1 | Loan = 1)
iii. P(Loan = 1) (the proportion of loan acceptors)
iv. P(CC = 1 | Loan = 0)
v. P(Online = 1 | Loan = 0)
vi. P(Loan = 0)
```{r}
#Probabilities
A <- 83/(83+196) #P(CreditCard = 1| Loan = 1)
A


B <- 165/(165+114) #P(Online = 1| Loan = 1)
B


C <- (279)/3000 #P(Loan = 1) 
C


D <- 790/(1931+790)#P(CC = 1 | Loan = 0) 
D


E <- 1644/(1644+1077) #P(Online = 1 | Loan = 0)
E

F <- 2721/3000 #P(Loan = 0) 
F

```

Q5 : Use the quantities computed above to compute the naive Bayes probability P(Loan = 1 | CC = 1,Online = 1).
```{r}
CalNaiBay <- (A*B*C/((A*B*C)+(D*E*F)))
CalNaiBay
```


Q6 : The probabiity in question B is 9.51% and the probability in question E is 9.3%. These are almost same.Naive Bayes assumes conditional independence between variables which makes the model less accurate. Hence 9.5% is more accurate estimate.

Q7 : Which of the entries in this table are needed for computing P(Loan = 1 | CC = 1, Online = 1)? Run naive Bayes on the data. Examine the model output on training data, and find the entry that corresponds to P(Loan = 1 | CC = 1, Online = 1). Compare this to the number you obtained in (E).
```{r, message= FALSE}
library(e1071)
NaiBay <- naiveBayes(Personal.Loan~.,data = Train_df)
NaiBay

```
A : Creditcard, Online and Personal Loan with the corresponding 0 and 1 values are required to compute P(Loan=1|CC=1,Online=1).The Naive Bayes model returned the conditional probabilities. The value corresponding to P(Loan = 1| CC = 1, Online = 1) is 0.093. The value we got in E is 0.093 as well. We have succefully implemented Naive Bayes on the data.




